Optimal strategies in mental rotation tasks

### 2013-05-14 man/final-project.tex
Move shepard rotation figure again
Reword the beginning of the computation model section

To compare the hypotheses, we need to compute the likelihood of each
hypothesis, i.e. $p(X_a,\ X_b\ \vert \ h_0)$ and $p(X_a,\ X_b\ \vert \
h_1)$.

The likelihood is easy to compute under $h_0$, because we assume that
$X_a$ and $X_b$ are independent. Thus:
\begin{equation}
  p(X_a,\ X_b\ \vert \ h_0)=p(X_a)p(X_b)
  \label{eq:lh-h0}
\end{equation}

When the configurations are the same, the likelihood becomes more
complicated:
\begin{equation} 
  p(X_a,\ X_b\ \vert \ h_1)=\int_R\int_M p(X_a) p(X_b\vert X_a,R,M) p(R) p(M)\ \mathrm{d}M\ \mathrm{d}R
\end{equation}

For a small number of vertices, we can compute the integral over $M$
by enumerating every possible mapping between $X_a$ and $X_b$. After
doing so, we obtain:
\begin{equation} 
  p(X_a,\ X_b\ \vert \ h_1)=\int_R p(X_a) p(X_b\vert X_a,R) p(R)\ \mathrm{d}R
\end{equation}

However, we cannot compute $p(X_b\vert X_a, R)$ directly. Instead, we
introduce a new variable $X_R$ denoting a mental image, which
approximates $RX_a$. The $X_R$ are generated sequentially by repeated
application of a function $\tau$:
\begin{align}
  X_R&=RX_a\nonumber \\
  &=\tau(X_{R-r}, r)\nonumber \\
  &=\tau(\tau(X_{R-2r}, r), r)\nonumber \\
  &\ldots{}\nonumber \\
  &=\tau^{(\frac{R}{r})}(X_a, r)
  \label{eq:tau}
\end{align} 
Where $r$ is a small angle, and $\tau^{(i)}$ indicates $i$ recursive
applications of $\tau$. Using this sequential function, we get:
\begin{align}
  p(X_a, X_b\ \vert \ h_1)&=\int_R \int_{X} p(X_b\vert X) p(X\vert X_a, R)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  x&= \int_R \int_X p(X_b\vert X)\delta(\tau^{(\frac{R}{r})}(X_a, r)-X)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  &= \int_R p(X_b\vert X_R)p(X_a)p(R)\ \mathrm{d}R
  \label{eq:lh-h1}
\end{align}

>>>>

To compare the hypotheses, we need to compute the posterior:
\begin{equation}
p(h_i\ \vert\ X_a, X_b)\propto p(X_a, X_b\ \vert\ h_i)p(h_i)
\end{equation}
Assuming the hypotheses are equally likely \textit{a priori}, the
prior term $p(h_i)$ will cancel out when comparing $h_0$ and $h_1$,
thus allowing us to focus on the likelihoods: 
\begin{align}
  p(X_a,\ X_b\ \vert \ h_0)&=p(X_a)p(X_b) \label{eq:lh-h0}\\
  p(X_a,\ X_b\ \vert \ h_1)&=\int_R\int_M p(X_a) p(X_b\vert X_a,R,M) p(R) p(M)\ \mathrm{d}M\ \mathrm{d}R \label{eq:lh-h1}
\end{align}
Under $h_0$, the likelihood is easy to compute because we assume that
$X_a$ and $X_b$ are independent (Equation \ref{eq:lh-h0}). However,
when the configurations are the same, the likelihood becomes more
complicated (Equation \ref{eq:lh-h1}). For a small number of vertices,
we can compute the integral over $M$ by enumerating every possible
mapping between $X_a$ and $X_b$. After doing so, we obtain:
\begin{equation} 
  p(X_a,\ X_b\ \vert \ h_1)=\int_R p(X_a) p(X_b\vert X_a,R) p(R)\ \mathrm{d}R
\end{equation}

However, we cannot compute $p(X_b\vert X_a, R)$ directly. Instead, we
introduce a new variable $X_R$ denoting a mental image, which
approximates $RX_a$. The $X_R$ are generated sequentially by repeated
application of a function $\tau$:
\begin{align}
  X_R&=RX_a\nonumber \\
  &=\tau(X_{R-r}, r)\nonumber \\
  &=\tau(\tau(X_{R-2r}, r), r)\nonumber \\
  &\ldots{}\nonumber \\
  &=\tau^{(\frac{R}{r})}(X_a, r)
  \label{eq:tau}
\end{align} 
Where $r$ is a small angle, and $\tau^{(i)}$ indicates $i$ recursive
applications of $\tau$. Using this sequential function, we get:
\begin{align}
  p(X_a, X_b\ \vert \ h_1)&=\int_R \int_{X} p(X_b\vert X) p(X\vert X_a, R)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  x&= \int_R \int_X p(X_b\vert X)\delta(\tau^{(\frac{R}{r})}(X_a, r)-X)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  &= \int_R p(X_b\vert X_R)p(X_a)p(R)\ \mathrm{d}R
\end{align}
